\chapter{Enhanced Population Coding for Rewarded Choices in the Medial Frontal Cortex of the Mouse}

% Header
\fancyhead[R]{\small{POPULATION CODING FOR REWARDED CHOICES}} %Running title

% Chapter Abstract
Instrumental behavior is characterized by the selection of actions based on the degree to which they lead to a desired outcome. However, we lack a detailed understanding of how rewarded actions are reinforced and preferentially implemented. In rodents, the medial frontal cortex is hypothesized to play an important role in this process, based in part on its capacity to encode chosen actions and their outcomes. We therefore asked how neural representations of choice and outcome might interact to facilitate instrumental behavior. To investigate this question, we imaged neural ensemble activity in layer 2/3 of the secondary motor region (M2) while mice engaged in a two-choice auditory discrimination task with probabilistic outcomes. Correct choices could result in one of three reward amounts (single, double or omitted reward), which allowed us to measure neural and behavioral effects of reward magnitude, as well as its categorical presence or absence. Single-unit and population decoding analyses revealed a consistent influence of outcome on choice signals in M2. Specifically, rewarded choices were more robustly encoded relative to unrewarded choices, with little dependence on the exact magnitude of reinforcement. Our results provide insight into the integration of past choices and outcomes in the rodent brain during instrumental behavior.\\


% Introduction
%\newpage
\input{Sections/Chapter2_Intro}

% Materials & Methods
%\newpage
\input{Sections/Chapter2_MatMeth}

% Results
%\newpage
\input{Sections/Chapter2_Results}

% Discussion
\input{Sections/Chapter2_Discussion}

% Acknowledgements
\input{Sections/Chapter2_Acknowledgments.tex}