\chapter{Neural Ensemble Dynamics during Flexible Sensorimotor Behavior}

% Header
\fancyhead[R]{\small{ENSEMBLE DYNAMICS DURING FLEXIBLE BEHAVIOR}} %Running title

% Chapter Abstract
\lettrine[lines=3]{T}{he} ability to shift between repetitive and goal-directed actions is a hallmark of cognitive control. Previous studies have reported that adaptive shifts in behavior are accompanied by changes in neural activity in frontal cortex. However, neural and behavioral adaptations can occur at multiple time scales, and their relationship remains poorly defined. Here we developed an adaptive sensorimotor decision-making task for head-fixed mice, requiring them to shift flexibly between multiple auditory–motor mappings. Two-photon calcium imaging of secondary motor cortex (M2) revealed different ensemble activity states for each mapping. When adapting to a conditional mapping, transitions in ensemble activity were abrupt and occurred before the recovery of behavioral performance. By contrast, gradual and delayed transitions accompanied shifts toward repetitive responding. These results demonstrate distinct ensemble signatures associated with the initiation and termination of sensory-guided behavior and suggest that M2 leads the engagement of goal-directed response strategies that require sensorimotor associations.
\newpage

% Introduction
%\newpage
\input{Sections/Chapter3_Intro}

% RESULTS
%\newpage
\input{Sections/Chapter3_Results}

% Discussion
\input{Sections/Chapter3_Discussion}

% Materials & Methods
%\newpage
\input{Sections/Chapter3_MatMeth}

% Acknowledgements
\input{Sections/Chapter3_Acknowledgments}

% Supplementary Figures
\input{Sections/Chapter3_SuppFigs}
