\chapter*{Acknowledgments}
% \begin{singlespace}

A multitude of people deserve my thanks for their support, guidance, and inspiration along this rather long and convoluted path toward a PhD.

Above all, my heartfelt gratitude goes to my family---especially to my wife, Jennifer, for her boundless love, support, and patience; to my children, Theodore and Gloria, for filling my heart with joy at just the very sight of them; to my Mom and Dad for their constant love, support, guidance, and inspiration; to my brothers, Jim, Robert, Daniel, Brian, and Steven, for a life-long bond of love, companionship, and adventure; and to my Godparents, Mary Lou Glad and James F. Shepard (1951--2019; RIP), for providing admirable examples of kindness, curiosity, grace, and courage. 

I wish to thank my wonderful mentors at Mount Sinai School of Medicine---Klaude Weiss and Betsy Cropper---who provided my first research opportunity, but more importantly, provided stellar examples of professional and intellectual mentorship; my friends and colleagues from MSSM, including Bjoern Ludwar, Jian Jing, Matthew Perkins, Andrew Dacks, Allyson Friedman, Brady Trexler, Sven Vilim, Mike Barry, Mike Burke, Mike Due, and the late great Vlad Brezina (1958--2016; RIP); as well as the faculty of Oberlin College for their generous teaching and mentorship---especially Todd and Dorit Ganson, Al MacKay, Mike Loose, Gigi Knight, and Chaelon Myme. 

I would like to thank my PhD advisor, Alex Kwan, for putting up with me as his first grad student. The training I have received under his mentorship will prove invaluable throughout my career as a scientist. I would also like to thank the members of the Kwan Lab, past and present, with whom I have had the pleasure of interacting over these many years---in particular: Victoria Phoumthipphavong, Marc Lozano, Farhan Ali, Florent Barthas, Al Kaye, George Sun, Hongli Wang, Huriye Atilgan, Jianna Cressy, Cayla Murphy, Heather Ortega, Neil Savalia, Melody Hu, Lingxiao Shao, Jen-Hau Yang, Clara Liao, Rachel Hannibal, Caroline Posner, Eugenia Zhukovsky, and Mark Dibbs. 

Many thanks to my thesis committee---Daeyeol Lee, Marina Picciotto, and Mike Crair---whose curiosity and guidance were vital to the completion of this work; as well as to my qualifying committee: Len Kaczmarek, George Dragoi, Ifat Levy, and Ralph DiLeone. I will be forever grateful for the privilege of studying and interacting with each of you.

Finally, I would like to thank the Yale Interdepartmental Neuroscience Program---and in particular, Carol Russo and Charlie Greer---for gathering together such an extraordinary and diverse community of developing scientists and cultivating an environment where we all can thrive.  